Analysis for Project

### 2021-11-23 analysis/analysis.Rmd
Add code chunk name

```{r}
model_add_cat <- glm(below_exp_grade~as.factor(year)+current_grade, 
                     data=acs, family=binomial)
model_add_cont <- glm(below_exp_grade~I(year-2010)+current_grade, 
                     data=acs, family=binomial)
model_inter_cont <- glm(below_exp_grade~I(year-2010)*current_grade, 
                     data=acs, family=binomial)
model_inter_cat <- glm(below_exp_grade~as.factor(year)*current_grade, 
                     data=acs, family=binomial)

>>>>

```{r models-year-grade}
model_add_cat <- glm(below_exp_grade~as.factor(year)+current_grade, 
                     data=acs, family=binomial)
model_add_cont <- glm(below_exp_grade~I(year-2010)+current_grade, 
                     data=acs, family=binomial)
model_inter_cont <- glm(below_exp_grade~I(year-2010)*current_grade, 
                     data=acs, family=binomial)
model_inter_cat <- glm(below_exp_grade~as.factor(year)*current_grade, 
                     data=acs, family=binomial)
